---
title: "Bayes' Rule"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE,
            warning=FALSE, message=FALSE)
```

## Models and Prior

Suppose we have two spinners -- one has four regions with areas 2, 1, 1, 2, and the second has four regions with areas 1, 2, 2, 1.  Suppose you choose one spinner at random and observe its spin.  Based on this spin you are going to revise your probabilities using Bayes' rule.

Here are pictures of the two spinners:

```{r}
library(TeachBayes)
spinners <- list(c(2, 1, 1, 2), c(1, 2, 2, 1))
many_spinner_plots(spinners)
```

### Exercise

You first choose one of the two spinners at random.  Create a new data frame `bayes_df` with two variables: `Model` contains the names of the two spinners, and `Prior` contains your initial probabilities of the spinner you chose. 


```{r prior, exercise=TRUE}
bayes_df <- data.frame(Model = 
                  paste("Spinner", c("A", "B")),
                       Prior = c())
bayes_df
```

## The Likelihoods

Next suppose you spin the unknown spinner once and you observe a 3 (in the blue region).

```{r}
library(TeachBayes)
spinners <- list(c(2, 1, 1, 2), c(1, 2, 2, 1))
many_spinner_plots(spinners)
```

```{r prepare-bayesdf}
bayes_df <- data.frame(Model = 
                  paste("Spinner", c("A", "B")),
                       Prior = c(0.5, 0.5))
```

### Exercise

Add a new variable `Likelihood` to the data frame `bayes_df` consisting of the likelihoods, the probabilities of observing a 3 (blue) for each of the two spinners.

```{r likelihood, exercise=TRUE, exercise.setup = "prepare-bayesdf"}
bayes_df$Likelihood <- c()
bayes_df
```

## The Posterior

Now we can update our probabilities of the two spinners by using Bayes' rule.

```{r}
library(TeachBayes)
spinners <- list(c(2, 1, 1, 2), c(1, 2, 2, 1))
many_spinner_plots(spinners)
```

```{r prepare-bayesdf2}
library(TeachBayes)
bayes_df <- data.frame(Model = 
                  paste("Spinner", c("A", "B")),
                       Prior = c(0.5, 0.5),
                  Likelihood = c(1/6, 1/3))
```

### Exercise

Use the `bayesian_crank` function with argument `bayes_df` to compute the updated probabilities of the spinners.

```{r posterior, exercise=TRUE, exercise.setup = "prepare-bayesdf2"}

```

## Compare Prior and Posterior

```{r prepare-bayesdf3}
library(TeachBayes)
bayes_df <- data.frame(Model = 
                  paste("Spinner", c("A", "B")),
                       Prior = c(0.5, 0.5),
                  Likelihood = c(1/6, 1/3))
bayes_df <- bayesian_crank(bayes_df)
```

### Exercise

The Prior and Posterior probabilities are stored in the data frame `bayes_df`.  Use the `prior_post_plot` function with argument `bayes_df` to compare the prior and posterior probabilities of the two spinners.

```{r graph, exercise=TRUE, exercise.setup = "prepare-bayesdf3"}

```
