---
title: "TeachBayes Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to TeachBayes}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=6, 
                      fig.height=4, fig.path='Figs/',
                      echo=TRUE, warning=FALSE, message=FALSE)
```

The `TeachBayes` package was written to assist in the teaching of a "Beginning Bayes" course.  There are a number of functions dealing with spinners, proportion, and mean inference.  The purpose of this introduction to give a simple example of all of the functions.  The material is divided into sections (1) Spinner Functions, (2) Inference for a Proportion, (3) Inference for a Mean, (4) Inference for Two Proportions and (5) Utilities

```{r}
library(TeachBayes)
```

### Spinner Functions

(spinner_data, spinner_likelihoods, spinner_plot, spinner_probs, dspinner, many_spinner_plots)

A useful randomization device is a spinner that is defined by a vector of areas.

```{r}
sp_regions <- c(2, 1, 1, 2)
```

1.  `spinner_plot` will construct a plot of the spinner.

```{r}
spinner_plot(sp_regions)
```

2.  `spinner_probs` displays the spinner probabilities:

```{r}
spinner_probs(sp_regions)
```
3.  `spinner_data` simulates spins from the spinner:

```{r}
spinner_data(sp_regions, nsim=20)
```

Suppose we define multiple spinners:

```{r}
sp1 <- c(1, 1, 1)
sp2 <- c(1, 2, 2, 1)
sp3 <- c(1, 1, 1, 1)
sp4 <- c(2, 2, 3, 3, 4)
```

4.  We can use `many_spinner_plots` to display all of the spinners.

```{r}
many_spinner_plots(list(sp1, sp2, sp3, sp4))
```

5.  Function `spinner_likelihoods` will compute a probability matrix for a group of spinners.  This is used in a Bayes' rule calculation.

```{r}
(LIKE <- spinner_likelihoods(list(sp1, sp2, sp3, sp4)))
```

6.  Function `dspinner` computes the likelhood function of spinners given a vector of spinner outcomes.

```{r}
dspinner(c(1, 3, 4, 1, 2), LIKE)
```

### Bayes' Rule

(bayesian_crank, prior_post_plot)

Given a data frame with variables `Model`, `Prior`, and `Likelihood`, function `bayesian_crank` computes the posterior probabilities.

```{r}
bayes_df <- data.frame(Model=paste("Spinner", 1:4),
                       Prior=rep(1/4, 4), 
                       Likelihood=dspinner(c(1, 2, 1), LIKE))
(bayes_df <- bayesian_crank(bayes_df))
```

Function `prior_post_plot` will display the prior and posterior probabilities.

```{r}
prior_post_plot(bayes_df)
```


### Inference for a Proportion

(beta_area, beta_data, beta_draw, beta_interval, beta_prior_post, beta_quantile, ChooseBeta)

1.  `beta_draw` displays a single beta curve

```{r}
beta_draw(c(10, 5))
```

2.  `beta_area` displays a beta area (probability)

```{r}
beta_area(.4, .6, c(10, 5))
```

3.  `beta_quantile` displays a beta quantile

```{r}
beta_quantile(.7, c(10, 5))
```

4.  `beta_interval` displays an equal-tails interval that contains a specific probability content

```{r}
beta_interval(.8, c(10, 5))
```

5.  `beta_data` simulates from a beta density

```{r}
beta_data(c(10, 5), nsim=20)
```

6.  `beta_prior_post` will graphically compare two beta curves such as a prior and posterior for a proportion

```{r}
beta_prior_post(c(4, 4), c(20, 10))
```

7.  Function `ChooseBeta` runs a Shiny app for selecting a beta curve based on knowledge of the prior median and prior 90th percentile.

### Inference for a Mean

(normal_area, normal_draw, normal_interval, normal_quantile, many_normal_plots, normal_update)

1.  Function `normal_area`  displays and computes a normal probability.

```{r}
normal_area(90, 105, c(100, 15))
```


2.  Function `normal_draw` will draw a single normal curve.

```{r}
normal_draw(c(100, 10))
```


3.  Function `normal_interval` will compute an equal tails probability interval.

```{r}
normal_interval(.8, c(100, 10))
```


4.  Function `normal_quantile` will compute and show graphically a normal quantile.

```{r}
normal_quantile(.3, c(100, 10))
```

5.  Function `many_normal_plots` will display many normal curves on the same graph.

```{r}
many_normal_plots(list(c(100, 10), c(110, 10), c(120, 10)))
```

6.  Function `normal_update` will give the posterior mean and standard deviation given the normal prior and the sample info.

```{r}
prior <- c(100, 10)
ybar <- 120
se <- 15
normal_update(prior, c(ybar, se))
```

```{r}
normal_update(prior, c(ybar, se), teach=TRUE)
```

### Inference for Two Proportions

(testing_prior, draw_two_p, two_p_update, twoproplike, two_p_summarize)

1.  Function `testing_prior` will construct a discrete prior for two proportions.

```{r}
testing_prior(.1, .5, 5)
```


2.  Function `draw_two_p` constructs a graph of a discrete distribution of two proportions.

```{r}
draw_two_p(testing_prior(.1, .5, 5))
```


3.  Function `two_p_update` will update a 2-proportion discrete prior with data.

```{r}
prior <- testing_prior(.1, .5, 5)
(post <- two_p_update(prior, c(2, 10), c(4, 10)))
```


4.  Function `twopropllike` computes a likelihood for two binomial proportions (currently this calculation is already in the two_p_update function).

5.  Function `two_p_summarize` will find the probability distribution for the difference in two proportions.

```{r}
prior <- testing_prior(.1, .5, 5)
post <- two_p_update(prior, c(2, 10), c(4, 10))
two_p_summarize(post)
```

### Utilities

1.  `bar_plot` constructs a frequency bar plot of numeric data

```{r}
bar_plot(spinner_data(c(1, 2, 3)))
```

2.  `prob_plot` constructs a plot of a discrete probability distribution

```{r}
prob_plot(data.frame(x=1:5, prob=c(.2, .3, .4, .1, .1)))
```


