---
title: "TeachBayes Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to TeachBayes}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=6, 
                      fig.height=4, fig.path='Figs/',
                      echo=TRUE, warning=FALSE, message=FALSE)
```

The `TeachBayes` package was written to assist in the teaching of a "Beginning Bayes" course.  There are a number of functions dealing with spinners and proportion inference.  The purpose of this introduction to give a simple example of all of the functions.  The material is divided into sections (1) Spinner Functions, (2) Inference for a Proportion, (3) Utilities

```{r}
library(TeachBayes)
```

### Spinner Functions

(spinner_data, spinner_likelihoods, spinner_plot, spinner_probs, dspinner, many_spinner_plots)

A useful randomization device is a spinner that is defined by a vector of areas.

```{r}
sp_regions <- c(2, 1, 1, 2)
```

1.  `spinner_plot` will construct a plot of the spinner.

```{r}
spinner_plot(sp_regions)
```

2.  `spinner_probs` displays the spinner probabilities:

```{r}
spinner_probs(sp_regions)
```
3.  `spinner_data` simulates spins from the spinner:

```{r}
spinner_data(sp_regions, nsim=20)
```

Suppose we define multiple spinners:

```{r}
sp1 <- c(1, 1, 1)
sp2 <- c(1, 2, 2, 1)
sp3 <- c(1, 1, 1, 1)
sp4 <- c(2, 2, 3, 3, 4)
```

4.  We can use `many_spinner_plots` to display all of the spinners.

```{r}
many_spinner_plots(list(sp1, sp2, sp3, sp4))
```

5.  Function `spinner_likelihoods` will compute a probability matrix for a group of spinners.  This is used in a Bayes' rule calculation.

```{r}
(LIKE <- spinner_likelihoods(list(sp1, sp2, sp3, sp4)))
```

6.  Function `dspinner` computes the likelhood function of spinners given a vector of spinner outcomes.

```{r}
dspinner(c(1, 3, 4, 1, 2), LIKE)
```

### Bayes' Rule

(bayesian_crank, prior_post_plot)

Given a data frame with variables `Model`, `Prior`, and `Likelihood`, function `bayesian_crank` computes the posterior probabilities.

```{r}
bayes_df <- data.frame(Model=paste("Spinner", 1:4),
                       Prior=rep(1/4, 4), 
                       Likelihood=dspinner(c(1, 2, 1), LIKE))
(bayes_df <- bayesian_crank(bayes_df))
```

Function `prior_post_plot` will display the prior and posterior probabilities.

```{r}
prior_post_plot(bayes_df)
```


### Inference for a Proportion

(beta_area, beta_data, beta_draw, beta_interval, beta_prior_post, beta_quantile, ChooseBeta)

1.  `beta_draw` displays a single beta curve

```{r}
beta_draw(c(10, 5))
```

2.  `beta_area` displays a beta area (probability)

```{r}
beta_area(.4, .6, c(10, 5))
```

3.  `beta_quantile` displays a beta quantile

```{r}
beta_quantile(.7, c(10, 5))
```

4.  `beta_interval` displays an equal-tails interval that contains a specific probability content

```{r}
beta_interval(.8, c(10, 5))
```

5.  `beta_data` simulates from a beta density

```{r}
beta_data(c(10, 5), nsim=20)
```

6.  `beta_prior_post` will graphically compare two beta curves such as a prior and posterior for a proportion

```{r}
beta_prior_post(c(4, 4), c(20, 10))
```

7.  Function `ChooseBeta` runs a Shiny app for selecting a beta curve based on knowledge of the prior median and prior 90th percentile.


### Utilities

1.  `bar_plot` constructs a frequency bar plot of numeric data

```{r}
bar_plot(spinner_data(c(1, 2, 3)))
```

2.  `prob_plot` constructs a plot of a discrete probability distribution

```{r}
prob_plot(data.frame(x=1:5, prob=c(.2, .3, .4, .1, .1)))
```


