---
title: "Two_Proportions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Two Proportions}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=6, 
                      fig.height=4, fig.path='Figs/',
                      echo=TRUE, warning=FALSE, message=FALSE)
```

The TeachBayes package has several functions to facilitate working with a discrete prior for two proportions.

```{r}
library(TeachBayes)
```

### Uniform Prior

Start with a uniform prior on (p1, p2), where each proportion takes on values .05, .15, ..., .95.

```{r}
prior <- testing_prior(.05, .95, 10,
                       uniform=TRUE)
```

Construct a graph of this distribution.

```{r}
draw_two_p(prior)
```

This finds the probability distribution of the difference in proportions p1 - p2, and plots the distribution.

```{r}
(diff_dist <- two_p_summarize(prior))
prob_plot(diff_dist)
```

Collect some data from two binomial samples.

```{r}
y1n1 <- c(10, 20)
y2n2 <- c(8, 24)
```

Update (find posterior):

```{r}
post <- two_p_update(prior, y1n1, y2n2)
```

Graph and summarize:

```{r}
draw_two_p(post)
```

```{r}
prob_plot(two_p_summarize(post))
```

### Testing Prior

```{r}
prior <- testing_prior(.05, .95, 10, pequal=0.5)
```

Construct a graph of this distribution and summarize.

```{r}
draw_two_p(prior)
```

```{r}
prob_plot(two_p_summarize(prior))
```

Collect some data from two binomial samples.

```{r}
y1n1 <- c(10, 20)
y2n2 <- c(8, 24)
```

Update (find posterior):

```{r}
post <- two_p_update(prior, y1n1, y2n2)
```

Graph and summarize:

```{r}
draw_two_p(post)
```

```{r}
prob_plot(two_p_summarize(post))
```
